---
title: "CARPS Reproducibility Report"
output:
  html_document:
    toc: true
    toc_float: true
---

```{r}
articleID <- "6-7-2014_PS" # insert the article ID code here e.g., "10-3-2015_PS"
reportType <- 'final'
pilotNames <- "Dawn Finzi, Kiara Sanchez" # insert the pilot's name here e.g., "Tom Hardwicke". If there are multiple pilots enter both names in a character string e.g., "Tom Hardwicke, Bob Dylan"
copilotNames <- "Ben Peloquin" # insert the co-pilot's name here e.g., "Michael Frank". If there are multiple co-pilots enter both names in a character string e.g., "Tom Hardwicke, Bob Dylan"
pilotTTC <- 180 # insert the pilot's estimated time to complete (in minutes, fine to approximate) e.g., 120
copilotTTC <- NA # insert the co- pilot's estimated time to complete (in minutes, fine to approximate) e.g., 120
pilotStartDate <- as.Date("11/02/17", format = "%m/%d/%y") # insert the pilot's start date in US format e.g., as.Date("01/25/18", format = "%m/%d/%y")
copilotStartDate <- as.Date("06/13/2018", format = "%m/%d/%y") # insert the co-pilot's start date in US format e.g., as.Date("01/25/18", format = "%m/%d/%y")
completionDate <- as.Date("", format = "%m/%d/%y") # copilot insert the date of final report completion (after any necessary rounds of author assistance) in US format e.g., as.Date("01/25/18", format = "%m/%d/%y")
```

-------

#### Methods summary: 

Researchers recruited 202 volunteers at a subway station in Toronto, Ontario, Canada. Half of the sample was traveling East, while the other half was traveling West. In a 2 (orientation: toward, away from) X 4 (station: Spadina, St. George, Bloor-Yonge, Sherbourne) design, each participant was randomly asked to estimate how far one of the four stations felt to them (1= very close, 7= very far). Authors conducted a 2 X 4 ANOVA on distance estimates, and then tested differences in distance estimates between East and West-bound groups for each individual station.

------

#### Target outcomes: 
> We carried out a 2 (orientation: toward, away from) × 4
(station: Spadina, St. George, Bloor-Yonge, Sherbourne)
analysis of variance (ANOVA) on closeness ratings, which
revealed no main effect of orientation, F < 1, and a main
effect of station, F(3, 194) = 24.10, p < .001, ηp
2 = .27. This main effect was qualified by the predicted interaction
between orientation and station, F(3, 194) = 16.28, p < .001, ηp2 = .20. We decomposed this interaction by the subjective-distance ratings between participants traveling
east and west for each of the four subway stations.
Westbound participants rated the stations to the west of
Bay Street as closer than did eastbound participants; this
effect was obtained for both the station one stop to the
west (St. George, p < .001, ηp2 = .28) and the station two
stops to the west (Spadina, p = .001, ηp2 = .20). The opposite
pattern held true for stations to the east of Bay Street.
Eastbound participants rated the stations to the east of
Bay Street as closer than did westbound participants; this
effect was obtained for both the station one stop to the
east (Bloor-Yonge, p = .053, ηp2 = .08) and the station two
stops to the east (Sherbourne, p < .001, ηp2 = .24). Figure 1 summarizes these results.

------

[The chunk below sets up some formatting options for the R Markdown document]

```{r global_options, include=FALSE}
knitr::opts_chunk$set(echo=TRUE, warning=FALSE, message=FALSE)
options(stringsAsFactors = FALSE)
```

## Step 1: Load packages

[Some useful packages are being loaded below. You can add any additional ones you might need too.]

```{r}
library(tidyverse) # for data munging
library(knitr) # for kable table formating
library(haven) # import and export 'SPSS', 'Stata' and 'SAS' Files
library(readxl) # import excel files
library(CARPSreports) # custom report functions
#library(TMB)
#library(sjstats) # computes eta squared for anova 
# install.packages("sjstats")
library(lsr)
```

```{r}
# Prepare report object. This will be updated automatically by the reproCheck function each time values are compared.
reportObject <- data.frame(dummyRow = TRUE, reportedValue = NA, obtainedValue = NA, valueType = NA, percentageError = NA, comparisonOutcome = NA, eyeballCheck = NA)
```

## Step 2: Load data

```{r}
d <- read_excel ("data/S1_Subway.xlsx")
```

## Step 3: Tidy data

Data set already in tidy format.

## Step 4: Run analysis

### Pre-processing

```{r}
# make variables factors
d$DIRECTION <- as.factor(d$DIRECTION)
d$STN_NAME<- as.factor(d$STN_NAME)

# subset dataframes for individual tests 
BY <- subset(d, STN_NAME == "B-Y")
SHER <- subset(d, STN_NAME == "SHER")
SPAD <-subset(d, STN_NAME == "SPAD")
STG<- subset(d, STN_NAME == "STG")


#Tried different contrasts to get reported main effect. No success. Same output with different contrasts.

# set levels
#d$STN_NAME = factor(d$STN_NAME,levels = c('SPAD', 'STG', 'B-Y', 'SHER'))

#backward difference coding
#contrasts(d$STN_NAME) = cbind(C1=c(-.75, .25, .25, .25), 
                           #C2=c(-.5, -.5, .5, .5),
                           #C3=c(-.25, -.25, -.25, .75)); contrasts(d$STN_NAME)

#other coding schemes
#contrasts(d$STN_NAME) = cbind(C1=c(-1, 1, 0, 0), 
                           #C2=c(0, 1, -1, 0),
                           #C3=c(-0, 0, 1, -1)); contrasts(d$STN_NAME)
```


# Descriptive statistics

```{r}
# Ns for each condition 
# West should = 101 ; East should = 101

N_cond <- d %>%
  group_by(DIRECTION) %>%
  summarise(N = length(DIRECTION))

kable(N_cond) #Ns are correct

summary_STN <- d %>%
  group_by(STN_NAME) %>%
  summarise(mean_distance = mean(DISTANCE), 
            sd_distance = sd(DISTANCE))
kable(summary_STN)

summary_DIRECTION <- d %>%
  group_by(DIRECTION) %>%
  summarise(mean_distance = mean(DISTANCE), 
            sd_distance = sd(DISTANCE))
kable(summary_DIRECTION) 

summary_int <- d %>%
  group_by(STN_NAME, DIRECTION) %>%
  summarise(mean_distance = mean(DISTANCE), 
            sd_distance = sd(DISTANCE))
kable(summary_int) #interaction summary
```

# Inferential statistics

```{r test1}
# 2 (DIRECTION) X 4 (STATION) ANOVA
# reported main effect of STATION: F(3, 194)= 24.10, p < .001
# reported interaction: F(3, 194)= 16.28, p < .001
t1 <- aov(DISTANCE ~ DIRECTION * STN_NAME, data=d)
summary(t1)

t1_lm <- lm(DISTANCE ~ DIRECTION * STN_NAME, data=d)
anova(t1_lm)#ran same test a different way to double check
```

```{r test1 repro check}
# MAIN EFFECT OBTAINED: F(3, 194)= 23.25, p < .001
# INTERACTION OBTAINED: SAME
reportObject <- reproCheck(reportedValue = "24.10", obtainedValue = 23.25, valueType = 'F')
#MINOR ERROR: 3.53%
```


```{r test 2}
#reported effect size (main effect of STR_NAME): 0.27
#reported effect size (STR_NAME X DIRECTION interaction):   0.20
# etaSQ_t1 = eta_sq(t1)
# etaSQ_t1 
kable(etaSquared(t1))
# etaSQ_t1a = eta_sq(t1a)
# etaSQ_t1a
kable(etaSquared(t1_lm))
```

```{r test 2 repro anova check}
reportObject <- reproCheck(reportedValue = "0.27", obtainedValue = 0.27, valueType = 'other')  # eta squared
reportObject <- reproCheck(reportedValue = "0.20", obtainedValue = 0.20, valueType = 'other')  # eta squared
```

### Station-specific analyses

```{r}
df_stations <- data.frame()
```

St. George
```{r st george}
# DISTANCE ~ DIRECTION for each station

#St. George
#reported p < .001
#reported effect size = 0.28
t2 <- aov(DISTANCE ~ DIRECTION, data=STG)
summary(t2)
#obtained p < .001
etaSQ_t2 <- etaSquared(t2)
etaSQ_t2 
#obtained effect size = 0.28
df_stations <- rbind(df_stations, 
                     data.frame("reportedValue"="0.001", "obtainedValue"=0.001, "valueType"="p", "station"="st george"))
df_stations <- rbind(df_stations, 
                     data.frame("reportedValue"="0.28", "obtainedValue"=0.28, "valueType"="other", "station"="st george"))
```

Spadina
```{r spadina}
#Spadina
#reported p = .001
#reported effect size = 0.20
t3 <- aov(DISTANCE ~ DIRECTION, data=SPAD)
summary(t3) 
#obtained p = .001
etaSQ_t3 = etaSquared(t3)
etaSQ_t3 
#obtained effect size = 0.20
df_stations <- rbind(df_stations, 
                     data.frame("reportedValue"="0.001", "obtainedValue"=0.001, "valueType"="p", "station"="spadina"))
df_stations <- rbind(df_stations, 
                     data.frame("reportedValue"="0.20", "obtainedValue"=0.20, "valueType"="other", "station"="spadina"))
```

Bloor-Yonge
```{r bloor-yonge}
#Bloor-Yonge
#reported p = .053
#reported effect size = 0.08
t4 <- aov(DISTANCE ~ DIRECTION, data=BY)
summary(t4) 
#obtained p = .053
etaSQ_t4 = etaSquared(t4)
etaSQ_t4 
#obtained effect size = 0.08

df_stations <- rbind(df_stations, 
                     data.frame("reportedValue"="0.053", "obtainedValue"=0.053, "valueType"="p", "station"="bloor-yonge"))
df_stations <- rbind(df_stations, 
                     data.frame("reportedValue"="0.08", "obtainedValue"=0.08, "valueType"="other",
                                "station"="bloor-yonge"))
```

Sherbourne
```{r sherbourne}
#Sherbourne
#reported p < .001
#reported effect size = 0.24
t5 <- aov(DISTANCE ~ DIRECTION, data=SHER)
summary(t5) 
#reported p < .001
etaSQ_t5 = etaSquared(t5)
etaSQ_t5 
#reported effect size = 0.24
df_stations <- rbind(df_stations, 
                     data.frame("reportedValue"="0.001", "obtainedValue"=0.001, "valueType"="p", "station"="sherbourne"))
df_stations <- rbind(df_stations, 
                     data.frame("reportedValue"="0.24", "obtainedValue"=0.24, "valueType"="other",
                                "station"="sherbourne"))
```

Run station reproChecks
```{r}
res <- mapply(reproCheck, df_stations$reportedValue, df_stations$obtainedValue, df_stations$valueType)
```

## Step 5: Conclusion

Overall, this dataset was well-organized, and it was easy to implement the statistical tests described in the original paper.

One conceptual issue that made it tricky to decide how to analyze the data was that the authors classified one of their ANOVA factors as "orientation" with the levels "toward" and "away from," when it appears they actually tested "direction," with the levels "East" and "West." Instead of running a 2 (toward, away from) X 4 (station) ANOVA as they described, they actually ran a 2 (East, West) X 4 (station) ANOVA and then tested whether orientation (toward, away from) influenced distance ratings by assessing differences between East and West groups for each station individually. This was a little confusing to parse out because I think I would have created a separate "orientation" variable and run an ANOVA with that based on their description of the design, but their secondary tests as well as Figure 1, which depicts orientation as "Traveling West" and "Traveling East" instead of "toward" and "away from" clued me in to the fact that they used direction instead of orientation. 


* `Minor Error`: Main effect of station. 3.73% difference on reported F-statistic. Note that this could be due to rounding.

```{r}
Author_Assistance = FALSE # was author assistance provided? (if so, enter TRUE)

Insufficient_Information_Errors <- 0 # how many discrete insufficient information issues did you encounter?

# Assess the causal locus (discrete reproducibility issues) of any reproducibility errors. Note that there doesn't necessarily have to be a one-to-one correspondance between discrete reproducibility issues and reproducibility errors. For example, it could be that the original article neglects to mention that a Greenhouse-Geisser correct was applied to ANOVA outcomes. This might result in multiple reproducibility errors, but there is a single causal locus (discrete reproducibility issue).

locus_typo <- 0 # how many discrete issues did you encounter that related to typographical errors?
locus_specification <- 0 # how many discrete issues did you encounter that related to incomplete, incorrect, or unclear specification of the original analyses?
locus_analysis <- 0 # how many discrete issues did you encounter that related to errors in the authors' original analyses?
locus_data <- 0 # how many discrete issues did you encounter that related to errors in the data files shared by the authors?
locus_unidentified <- 0 # how many discrete issues were there for which you could not identify the cause

Affects_Conclusion <- FALSE # Do any reproducibility issues encounter appear to affect the conclusions made in the original article? This is a subjective judgement, but you should taking into account multiple factors, such as the presence/absence of decision errors, the number of target outcomes that could not be reproduced, the type of outcomes that could or could not be reproduced, the difference in magnitude of effect sizes, and the predictions of the specific hypothesis under scrutiny.
```

```{r}
reportObject <- reportObject %>%
  filter(dummyRow == FALSE) %>% # remove the dummy row
  select(-dummyRow) %>% # remove dummy row designation
  mutate(articleID = articleID) %>% # add the articleID 
  select(articleID, everything()) # make articleID first column

# decide on final outcome
if(any(reportObject$comparisonOutcome != "MATCH") | Insufficient_Information_Errors > 0){
  finalOutcome <- "Failure without author assistance"
  if(Author_Assistance == T){
    finalOutcome <- "Failure despite author assistance"
  }
}else{
  finalOutcome <- "Success without author assistance"
  if(Author_Assistance == T){
    finalOutcome <- "Success with author assistance"
  }
}

# collate report extra details
reportExtras <- data.frame(articleID, pilotNames, copilotNames, pilotTTC, copilotTTC, pilotStartDate, copilotStartDate, completionDate, Author_Assistance, finalOutcome, Insufficient_Information_Errors, locus_typo, locus_specification, locus_analysis, locus_data, locus_unidentified)

# save report objects
if(reportType == "pilot"){
  write_csv(reportObject, "pilotReportDetailed.csv")
  write_csv(reportExtras, "pilotReportExtras.csv")
}

if(reportType == "final"){
  write_csv(reportObject, "finalReportDetailed.csv")
  write_csv(reportExtras, "finalReportExtras.csv")
}
```

# Session information

```{r session_info, include=TRUE, echo=TRUE, results='markup'}
devtools::session_info()
```
