---
title: "CARPS Reproducibility Report"
output:
  html_document:
    toc: true
    toc_float: true
---

#### Article ID: CARPS_6-7-2014_PS
#### Pilot 1: Kiara Sanchez
#### Co-pilot: Dawn Finzi
#### Start date: [11/02/17]
#### End date: [11/05/17]   

-------

#### Methods summary: 
[Write a brief summary of the methods underlying the target outcomes written in your own words]

------

#### Target outcomes: 
> We carried out a 2 (orientation: toward, away from) × 4
(station: Spadina, St. George, Bloor-Yonge, Sherbourne)
analysis of variance (ANOVA) on closeness ratings, which
revealed no main effect of orientation, F < 1, and a main
effect of station, F(3, 194) = 24.10, p < .001, ηp
2 = .27. This main effect was qualified by the predicted interaction
between orientation and station, F(3, 194) = 16.28, p < .001, ηp2 = .20. We decomposed this interaction by the subjective-distance ratings between participants traveling
east and west for each of the four subway stations.
Westbound participants rated the stations to the west of
Bay Street as closer than did eastbound participants; this
effect was obtained for both the station one stop to the
west (St. George, p < .001, ηp2 = .28) and the station two
stops to the west (Spadina, p = .001, ηp2 = .20). The opposite
pattern held true for stations to the east of Bay Street.
Eastbound participants rated the stations to the east of
Bay Street as closer than did westbound participants; this
effect was obtained for both the station one stop to the
east (Bloor-Yonge, p = .053, ηp2 = .08) and the station two
stops to the east (Sherbourne, p < .001, ηp2 = .24). Figure 1 summarizes these results.

------

[The chunk below sets up some formatting options for the R Markdown document]

```{r global_options, include=FALSE}
knitr::opts_chunk$set(echo=TRUE, warning=FALSE, message=FALSE)
```

## Step 1: Load packages

[Some useful packages are being loaded below. You can add any additional ones you might need too.]

```{r}
library(tidyverse) # for data munging
library(knitr) # for kable table formating
library(haven) # import and export 'SPSS', 'Stata' and 'SAS' Files
library(readxl) # import excel files
library(CARPSreports) # custom report functions
```

## Step 2: Load data

```{r}
```

## Step 3: Tidy data

```{r}
```

## Step 4: Run analysis

### Pre-processing

[you can remove this section if no pre-processing is required]

```{r}
```

### Descriptive statistics

```{r}
```

### Inferential statistics

```{r}
```

## Step 5: Conclusion

[Include the carpsReport function below]

```{r}
# You can delete this commented text for your report, it is here to serve as a guide.
# Use the carpsReport() function in this code chunk.
# Here is a guide to the arguments you should include in the function:
# Report_Type: Enter 'pilot' or 'final'
# Article_ID: Enter the article's unique ID code
# Insufficient_Information_Errors: Enter the number of Insufficient Information Errors
# Decision_Errors Enter: the number of decision errors
# Major_Numerical_Errors: Enter the number of major numerical errors
# Time_to_Complete: Enter the estimated time to complete the report in minutes
# Author_Assistance: Enter whether author assistance was required (TRUE/FALSE)
# FOR EXAMPLE:
# carpsReport(Report_Type = "pilot", 
#             Article_ID = "ABhgyo", 
#             Insufficient_Information_Errors = 0, 
#             Decision_Errors = 1, 
#             Major_Numerical_Errors = 4, 
#             Time_to_Complete = 120, 
#             Author_Assistance = TRUE)
```

[Please also include a brief text summary describing your findings. If this reproducibility check was a failure, you should note any suggestions as to what you think the likely cause(s) might be.]

[This function will output information about the package versions used in this report:]

```{r session_info, include=TRUE, echo=TRUE, results='markup'}
devtools::session_info()
```
